Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-04-03 paper2.tex
edits

The lens-model masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$.  Preliminary estimates of the stellar masses show
(with two outliers) a smaller spread in stellar mass: a factor of a
few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
fraction declines sharply as total mass increases.  The most massive
system is J1434+522 (SW05).  The two low-mass outliers are J0206-095
(SW19) and J2217+015 (SW42).  If they are indeed lenses, they are
probing an interesting regime of very low star-formation efficiency.

>>>>

The lens-model masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$.  Preliminary estimates of the stellar masses show
(with two outliers) a smaller spread in stellar mass: a factor of a
few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
fraction declines sharply as total mass increases.  The highest-mass
system with a convincing model is J1434+522 (SW05).  The two low-mass
outliers are J0206-095 (SW19) and J2217+015 (SW42); if these two are
indeed lenses, they are probing an interesting regime of very low
star-formation efficiency.
